---
title: "MPG"
author: "Puttipong Ch"
date: "2024-02-12"
output: html_document
---

This project use mpg dataset 

install package
```{r,message=FALSE}
library(tidyverse)
library(ggplot2)
data(mpg)
```


```{r}
head(mpg)
```


```{r}
ggplot(mpg,aes(x=cty))+
  geom_histogram(bins=15)+
  theme_minimal()
```

```{r}
ggplot(mpg,aes(x=hwy))+
  geom_histogram(bins=10)+
  theme_minimal()
```



# The Fuel : 
- e: ethanol E85, note(subset(mpg, fl=="e") pulls up only "new" american cars, and that fuel economy is much lower than the corresponding presumably gasoline models, which lines up with the lower energy content of ethanol)
- d: diesel
- r: regular
- p: premium
- c: CNG (note as far as I know the civic is basically the only passenger car that runs on CNG in the US).

```{r}
ggplot(mpg,aes(cty,hwy,color=fl))+
  geom_point(alpha=0.5,size=3)+
  theme_minimal()
```



```{r}
ggplot(mpg ,aes(class,hwy))+
  geom_boxplot()+
  theme_minimal()
```


```{r}
ggplot(mpg ,aes(fl,hwy))+
  geom_boxplot()+
  facet_wrap(~fl,nrow=1)
  theme_minimal()
```




```{r}
ggplot(mpg ,aes(fl))+
  geom_bar()+
  theme_minimal()
```


mpg%>%
    select(hwy,fl) %>%
    group_by(fl)%>%
    summarise(hwy_avg=mean(hwy))


```{r}
ggplot(mpg%>%
         select(hwy,fl) %>%
         group_by(fl)%>%
         summarise(hwy_avg=mean(hwy)),aes(fl,hwy_avg))+
  geom_col()+
  theme_minimal()
```



```{r}
ggplot(mpg%>%
         select(cty,fl) %>%
         group_by(fl)%>%
         summarise(cty_avg=mean(cty)),aes(fl,cty_avg))+
  geom_col()+
  theme_minimal()
```
















